What is an Ancestral Recombination Graph?

### 2022-03-02 paper.tex
Change breakpoint numbers to match diagram

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
The Ancestral Recombination Graph defined in terms of genomes embedded
in a pedigree. (a) Diploid individuals, visualised in a highly inbred pedigree and
labelled $i_1$ to $i_8$, contain both paternal (left) and maternal (right) genomes
labelled \textsf{A} to \textsf{P}. Black lines show transmission paths connecting
genomes in the current generation (\textsf{A} to \textsf{D}) with their ancestors.
Two recombination breakpoints, at positions 3 and 6 mean that genomes \textsf{A}
and \textsf{C} are independent recombinants of the paternal genomes \textsf{E}
and \textsf{F}: the region of genome transmitted through each edge is shown in
these cases. Where genomes merge into a common ancestor, the merged region
is shown darker, until all genomic regions are fully coalesced in genome \textsf{N}
(b) The equivalent genome ARG, where there is a single type of node (representing
a genome) along with annotations on all edges; annotations showing partial
transmission are highlighted in bold. Recombination, such as that causing the
breakpoint at position 3, is associated with two parent genomes (\textsf{E} and 
\textsf{F}) and a child genome (the recombinant, \textsf{A}).
(c) The edge-annotated genome ARG in (b) fully defines the
local relationships along the genome, as shown in the local
or ``marginal'' trees.
}
\end{figure}

>>>>

\begin{figure}
\begin{center}
    \includegraphics[width=\textwidth]{illustrations/arg-in-pedigree}
\end{center}
\caption{\label{fig-arg-in-pedigree}
% TODO caption needs another pass. One the full section has been written
% it'll be clearer what we need to say in the caption vs the text.
The Ancestral Recombination Graph defined in terms of genomes embedded
in a pedigree. (a) Diploid individuals, visualised in a highly inbred pedigree and
labelled $i_1$ to $i_8$, contain both paternal (left) and maternal (right) genomes
labelled \textsf{A} to \textsf{P}. Black lines show transmission paths connecting
genomes in the current generation (\textsf{A} to \textsf{D}) with their ancestors.
Two recombination breakpoints, at positions 2 and 7 mean that genomes \textsf{A}
and \textsf{C} are independent recombinants of the paternal genomes \textsf{E}
and \textsf{F}: the region of genome transmitted through each edge is shown in
these cases. Where genomes merge into a common ancestor, the merged region
is shown darker, until all genomic regions are fully coalesced in genome \textsf{N}
in the oldest generation.
(b) The equivalent genome ARG, where there is a single type of node (representing
a genome) along with annotations on all edges; annotations showing partial
transmission are highlighted in bold. Recombination, such as that causing the
breakpoint at position 7, is associated with two parent genomes (\textsf{E} and 
\textsf{F}) and a child genome (the recombinant, \textsf{C}).
(c) The edge-annotated genome ARG in (b) fully defines the
local relationships along the genome, as shown in the local
or ``marginal'' trees.
}
\end{figure}
